Ace inhibitors LPA

### 2021-03-04 r_notebooks/ace_mlm_dan.Rmd
Ace inhibitor multilevel modelling

gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid),
         dispensing = as_factor(dispensing),
         cluster = str_replace_all(cluster, " ", "_"),
         cluster = str_remove_all(cluster, "[/&]"),
         cluster = as_factor(cluster),
         hboard = as_factor(str_remove_all(hboard, "W110000")),
         gp_load = npat/ngp) %>% 
  filter(year == 2020) %>% 
  ungroup() %>% 
  janitor::clean_names()
unique(gp$cluster)
differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

@@

proportions <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug),
         prop = (prop * 100) - 100) %>% 
  select(drug, regional_unit, datename, prop)

@@

@@

```{r, mar-m1-cluster-model}
mar_mlm1 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE))

@@

```{r, mar-m1-cluster-convergence}
mar_mlm1 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_p_fem", "b_pm_65", "b_dispensingYes",
                          "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 2000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")

```{r, mar-m1-cluster-params}
mar_mlm1_params %>% 
  kable(digits = 2)

mar_mlm1 %>% 
  sjstats::tidy_stan()
```

@@

```{r, mar-mlm2-cluster-model}
mar_mlm2 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15, adapt_delta = .999))

@@

* Removing gp_load as 0 effect and 0 variance

```{r, mar-mlm3-cluster-model}
mar_mlm3 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 +
              (1 + p_fem + pm_65 + dispensing + wimd2019|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15, adapt_delta = .999))

mar_mlm3_params <- modelParams(mar_mlm3)
```

```{r, mar-m3-cluster-convergence}
mar_mlm3 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_p_fem", "b_pm_65", "b_dispensingYes",
                          "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 2000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r, mar-m3-cluster-params}
mar_mlm3_params %>% 
  kable(digits = 2)
```

@@

```{r, apr-m1-cluster-model, include=FALSE}
apr_mlm1 <- brm(april ~ 1 + march +
                 p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 4000, seed = 123, save_pars = save_pars(all = TRUE))

@@

```{r, apr-m1-cluster-convergence}
apr_mlm1 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_march", "b_p_fem", "b_pm_65", 
                          "b_dispensingYes", "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 2000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

@@

```{r, apr-m2-cluster-model, include=FALSE}
apr_mlm2 <- brm(april ~ 1 + march +
                  p_fem + pm_65 + dispensing + wimd2019 + gp_load +
                  (1 + march +
                     p_fem + pm_65 + dispensing + wimd2019 + gp_load|cluster), 
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15, adapt_delta = .999))

>>>>

gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid),
         dispensing = as_factor(dispensing),
         cluster = as_factor(cluster),
         hboard = as_factor(str_remove_all(hboard, "W110000")),
         gp_load = npat/ngp) %>% 
  ungroup() %>% 
  janitor::clean_names()

differences_files <- 
  list.files("../data/differences/")
names(differences_files) <- 
  str_remove_all(differences_files, "_discreps.rds")

@@

proportions <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = as_factor(drug)) %>% 
  select(drug, regional_unit, datename, prop)

@@

## Disease profiles

```{r}
df <- select(filter(gp, year == "2020"), p_fem:flu)
psych::fa.parallel(df)
five_fac <- psych::fa(df, nfactors = 4, rotate = "varimax")
print(five_fac$loadings, cutoff = .2)

dis_pca <- psych::principal(df, nfactors = 3, scores = TRUE)
plot(dis_pca$values)
dis_pca$rotation
dis_pca_scores <- bind_cols(practice_id = filter(gp, year == "2020")$practice_id, dis_pca$scores)

# 2d plot
x <- dis_pca$loadings[,1]
y <- dis_pca$loadings[,2]
z <- dis_pca$loadings[,3]

pca_plot_df <- bind_cols(dis = names(x), x = x, y = y, z = z)

ggplot(aes(x = x, y = y), data = pca_plot_df) +
  geom_text(aes(label = dis))

ggplot(aes(x = x, y = z), data = pca_plot_df) +
  geom_text(aes(label = dis))

# 3d plot
plotly::plot_ly(x=x, y=y, z=z, data = pca_plot_df,
                type="scatter3d", mode="text", text = ~dis)
```

@@

```{r, mar-m1-cluster-model}
mar_mlm1 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1|cluster),  
      data = mlm_df, 
      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE))

@@

```{r, mar-m1-cluster-convergence}
mar_mlm1 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_p_fem", "b_pm_65", "b_dispensingYes",
                          "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 1000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

```{r, mar-m1-cluster-params}
mar_mlm1_params %>% 
  kable(digits = 2)
```

@@

```{r, mar-mlm2-cluster-model}
mar_mlm2 <- brm(march ~ 1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1 + p_fem + pm_65 + dispensing + wimd2019 + gp_load|cluster),  
      data = mlm_df, 
      warmup = 2000, iter = 6000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15))

@@

@@

```{r, apr-m1-cluster-model, include=FALSE}
apr_mlm1 <- brm(april ~ 1 + march +
                 p_fem + pm_65 + dispensing + wimd2019 + gp_load +
              (1|cluster),  
      data = mlm_df, 
      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE))

@@

```{r, apr-m1-cluster-convergence}
apr_mlm1 %>% 
  ggs() %>% 
  filter(Parameter %in% c("b_Intercept", "b_march", "b_p_fem", "b_pm_65", 
                          "b_dispensingYes", "b_wimd2019", "b_gp_load")) %>% 
  ggplot(aes(x = Iteration, y = value, col = as.factor(Chain))) +
  geom_line() +
  geom_vline(xintercept = 1000) +
  facet_grid(Parameter ~ .,
             scale = "free_y",
             switch = "y")
```

@@

```{r, apr-m2-cluster-model, include=FALSE}
apr_mlm2 <- brm(march ~ 1 + march +
                  p_fem + pm_65 + dispensing + wimd2019 + gp_load +
                  (1 + march +
                     p_fem + pm_65 + dispensing + wimd2019 + gp_load|cluster), 
      data = mlm_df, 
      warmup = 1000, iter = 3000, seed = 123, save_pars = save_pars(all = TRUE),
      control = list(max_treedepth = 15))
